\documentclass[margin,line]{res}

% File produced by Jeremy West
% This file may be distributed and/or modified:
%   1. under the LaTeX Project Public License and/or
%   2. under the GNU Public License.

% NOTE: you also need the (included) res.cls class file to compile this document
% Either place the .cls file in the same directory (folder) as this .tex file, or install it globally for your LaTeX distribution (search online for how to do so).

\usepackage{setspace}                                    % Allows for custom margins, etc.
\usepackage{fullpage}                                    % Use the full page
\usepackage[latin9]{inputenc}                            % Font definition and input type
\usepackage[T1]{fontenc}                                 % Font output type 
\usepackage{mmap}                                        % Allows glyphs (e.g. ff) to copy properly (ASCII)
\usepackage{textcomp}                                    % Supports many symbols such as copyright
\usepackage{color}                                       % Allow for colored text, etc.
\usepackage[]{hyperref}                                  % Allow hyperlinks (internal and external)
\hypersetup{                                             % Custom hyperlink settings
    pdffitwindow=false,                                  % Window fit to page when opened
    pdfstartview={XYZ null null 1.00},                   % Fits the zoom of the page to 100%
    pdfnewwindow=true,                                   % Links in new window
    colorlinks=true,                                     % false: boxed links; true: colored links
    linkcolor=black,                                     % Color of internal links (black is necessary for printing quality)
    citecolor=black,                                     % Color of links to bibliography
    urlcolor=black,                                      % Color of external links
    pdfauthor = {Your Name},
    pdfkeywords = {Your Keywords},
    pdftitle = {Your Name: Curriculum Vitae},
    pdfsubject = {Curriculum Vitae},
    pdfpagemode = UseNone}
    
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight}

	\addtolength{\topmargin}{-.3in}
	\addtolength{\textheight}{0.6in} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
      
\usepackage{datetime}                                    % Custom date format for date field
\newdateformat{mydate}{\monthname[\THEMONTH] \THEYEAR}   % Defining month year date format

\usepackage{fancyhdr}                                    % Used for custom page headers
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.5pt} 
\rhead{\footnotesize Wei Lin \thepage} %header at the right
\headsep = 0.5cm
% FIRST PAGE ONLY (redefine the plain pagestyle)
\fancypagestyle{plain}{
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} 
\headsep = 0.0cm
\rhead{\footnotesize Curriculum Vitae updated \mydate \today}
}


\begin{document}

\name{ {\LARGE Wei Lin} \vspace*{.1in}}

\begin{resume}
\thispagestyle{plain} % to use first page footer

\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{0.20in}p{2.75in}p{2.75in}}
 & 10523 Ashton Ave Ave unit 101             & Mobile: (321)-948-8592 \\            
 & Los Angeles, CA 90024   & E-mail: \href{mailto: Your email}{ weilin0929@gmail.com} \\                
\end{tabular}

% You may of course add to or remove from this list of sections as needed

\section{\sc Research Interests}
\begin{list1}
\item[] Machine Learning, Game Theory, Multi-Agent Systems, Optimization, Energy Systems
\end{list1}

\section{\sc Education}
\begin{list1}
\item[] University of Central Florida, Orlando, FL\\
\vspace*{-.1in}
\begin{list1}
\item[] \textbf{Ph.D. in Electrical Engineering} (12/2013)
\item[] Dissertation: ``Differential Games for Multi-agent Systems under Distributed Information''
\vspace*{.1in}
\end{list1}

\item[] Boston University, Boston, MA
\begin{list1}
\item[] \textbf{M.S. in Electrical Engineering} (5/2009)
\vspace*{.1in}
\end{list1}

\item[] Tongji University, Shanghai, China
\begin{list1}
\item[] \textbf{B.Eng. in Automation} (6/2007)
\end{list1}
\end{list1}


\section{\sc Professional Experience}
\begin{list1}

\item[] Inspire Energy, Santa Monica, CA
\vspace*{.05in}
\begin{list1}
\item[] \textbf{Senior Data Scientist} (3/2017 to present)
\item[] Develop machine learning algorithms for customer load forecasting and churn prediction.
\item[] \textbf{Data Scientist} (11/2015 to 3/2017)
\item[] Architected business operating model for financial forecasting and portfolio management.
\vspace*{.1in}
\end{list1}

\item[] Western Digital Corporation, Irvine, CA
\vspace*{.05in}
\begin{list1}
\item[] \textbf{Staff Firmware Engineer} (1/2014 to 11/2015)
\item[] Prototyped machine learning algorithms for hard drive failure prediction and developed sensor fusion and adaptive filtering algorithms for hard drive vibration control.
\vspace*{.1in}
\end{list1}

\item[] University of Central Florida, Orlando, FL
\vspace*{.05in}
\begin{list1}
\item[] \textbf{Research Assistant} (1/2010 to 12/2013)
\item[] Conducted research on multi-agent dynamic systems under distributed information with applications to unmanned aerial vehicles, distributed generation system optimization.
\vspace*{.1in}
\end{list1}

\item[] Alcatel-Lucent Shanghai Bell, Shanghai, China
\vspace*{.05in}
\begin{list1}
\item[] \textbf{Electronics Designer} (7/2009 to 11/2009)
\item[] Designed embedded rail signal control system hardware with high safety standard. 
\end{list1}

\end{list1}


\section{\sc Teaching Experience}
\begin{list1}
\item[] University of Central Florida, Orlando, FL
\vspace*{.05in}
\begin{list1}
\item[] \textbf{Teaching Assistant}
\begin{list2}
\item[] \textit{EEL 4140 Analog Filter Design} (Fall 2011).
\item[] Instructed lab sessions and administered all grades
\item[] \textit{EEL 4750 Digital Signal Processing Fundamentals} (Fall 2010)
\item[] Instructed lab sessions and administered all grades
\end{list2}
\end{list1}
\end{list1}


\section{\sc Publications}
\begin{enumerate}
\item W. Lin, ``Distributed UAV formation control using differential game approach,'' \emph{Aerospace Science and Technology}, vol. 35, pp. 54-62, 2014.
\vspace*{0.3cm}

\item A. Maknouninejad, W. Lin, H. Harno, Z. Qu, and M. Simaan, ``Cooperative control for self-organizing microgrids and game strategies for optimal dispatch of distributed renewable generations,'' \emph{Energy Systems}, vol. 3, no. 1, pp. 23-60, 2012.
\vspace*{0.3cm}

\item W. Lin, ``Differential games for multi-agent systems under distributed information'', \emph{Ph.D. dissertation}, University of Central Florida, 2013
\vspace*{0.3cm}

\item W. Lin, Z. Qu, and M. Simaan, ``Nash strategies for pursuit-evasion differential games involving limited observations,'' \emph{IEEE Transactions on Aerospace and Electronic Systems}, vol. 51, no. 2, pp. 1347-1356, 2015
\vspace*{0.3cm}

\item W. Lin, Z. Qu, and M. Simaan, ``Distributed game strategy design with application to multi-agent formation,'' \emph{53rd IEEE Conference on Decision and Control}, Los Angeles, CA, pp. 433-438, 2014.
\vspace*{0.3cm}

\item W. Lin, Z. Qu, and M. Simaan, ``Multi-pursuer single-evader differential games with limited observations,''  \emph{American Control Conference}, Washington D.C., USA, pp. 2711-2716, 2013
\vspace*{0.3cm}

\item A. Maknouninejad, W. Lin, and Z. Qu ``Optimum design and analysis of the cooperative control applied to the distributed generators control in smart grids,'' \emph{IEEE PES Innovative Smart Grid Technologies (ISGT)}, pp. 1-6, 2013.
\vspace*{0.3cm}

\item W. Lin, Z. Qu, and M. Simaan, ``A design of entrapment strategies for the distributed pursuit-evasion game,'' \emph{18th IFAC World Congress}, Milan, Italy, 2011, pp. 9334--9339.
\vspace*{0.3cm}

\item W. Lin, Z. Qu, and M. Simaan, ``A Design of Distributed Nonzero-Sum Nash Strategies,'' \emph{49th IEEE Conferenceon Decision and Control}, Atlanta, GA, 2010, pp. 6305--6310.
\end{enumerate}

\section{\sc Professional Membership}
\begin{list1}
\item[] IEEE Control System Society
\end{list1}

\section{\sc Professional Activity}
\begin{list1}
\item[] Peer Reviewer:
\vspace*{.05in}
\begin{list2}
\item IEEE Transcation on Automatic Control
\item Aerospcae Science and Technology
\item Automatica
\item IEEE Access
\item Optimal Control, Applications and Methods
\item Journal of Control and Decision
\item International Journal of Control, Automation and Systems 
\item Journal of Guidance, Control, and Dynamics
\item Robotics and Autonomous Systems
\item Journal of Supercomputing
\item American Control Conference
\item IEEE Conference on Decision and Control
\item ASME Conference on Information Storage and Processing Systems
\end{list2}
\vspace*{.1in}
\item[] Volunteer:
\begin{list2}
\item 50th IEEE Conference on Decision and Control, IEEE, Orlando, FL, 2012
\end{list2}
\end{list1}


\section{\sc Presentations} 
\begin{list1}
\item[] ``Distributed game strategy design with application to multi-agent formation,'' in \emph{53rd IEEE Conference on Decision and Control}, Los Angeles, CA, USA, 2014.
\vspace*{0.3cm}
\item[] ``Multi-pursuer single-evader differential games with limited observations,'' in \emph{American Control Conference}, Washington D.C., USA, 2013.
\vspace*{0.3cm}
\item[] ``A Design of Distributed Game Strategies for Autonomous Vehicles,'' in \emph{1st National Control Engineering Student Workshop}, University of Maryland, MD, 2011.
\vspace*{0.3cm}
\item[] ``A Design of Distributed Nonzero-Sum Nash Strategies,'' in \emph{49th IEEE Conferenceon Decision and Control}, Atlanta, GA, USA, 2010. 
\end{list1}


\section{\sc Awards and Certificates} 
\begin{list1}
\item[] Third-Class Scholarship, Tongji University, 2006.
\item[] Third-Class Scholarship, Tongji University, 2004.
\item[] Li Zutong Scholarship, Xiaoshi Middle School, 2003.
\end{list1}

\section{\sc References}
\vspace{.05in}
\begin{tabular}{@{}p{0.20in}p{2.5in}p{3in}}
& Prof. Zhihua Qu                           
& Prof. Marwan A. Simaan \\
& Department of EECS                           
& Department of EECS \\
& University of Central Florida                       
& University of Central Florida \\
& 4000 Central Florida Blvd.                           
& 4000 Central Florida Blvd.\\
&Orlando, Florida, 32816
&Orlando, Florida, 32816\\
& Phone: (407) 823-5976
& Phone: (407) 882-2220 \\
& E-mail: \href{mailto:email@email.edu}{qu@ucf.edu} 
& E-mail: \href{mailto:email@email.edu}{simaan@eecs.ucf.edu} \\
&&\\
&Dr. Edward Tu 
&Dr. Jie Yu \\
&Advance Technology Organization
&Advance Technology Organization\\
& Western Digital Corporation
& Western Digital Corporation\\
&3355 Michelson Drive, Suite 100 
&3355 Michelson Drive, Suite 100\\
&Irvine, California, 92612
&Irvine, California, 92612\\
& Phone: (949) 648-9809
& E-mail: \href{mailto: Your email}{jie.yu@wdc.com}\\
& E-mail: \href{mailto: Your email}{edward.tu@wdc.com}\\
&&\\
&Prof. Michael Caramanis&\\  
&Division of Systems Engineering&\\
&Boston University&\\
&One Silber Way&\\
&Boston, MA 02215&\\
&Phone: (617) 353-3247&\\
&E-mail: \href{mailto: Your email}{mcaraman@bu.edu}&
\end{tabular}





\end{resume}
\end{document}
